Using vector space models based on LDA and LSA for automatically grading exam questions

### 2018-06-21 tex/article.tex
Refined the discussion of letting the model grade good and bad answers, and leaving the rest for the lecturer to grade.

The next answer is an example of an answer that the lecturer had given 0 points (i.e., the lowest possible score):

@@

Even given the limitations described above, a model does not have to be perfect in order to be of potential use. For example, upon inspecting the individual models' results, I could see that whenever the model had assigned a zero to a student answer, the lecturer had also assigned a zero. Thus, the current models \textit{are} good enough to automatically detect which answers are worth zero points. A lecturer could use this information to focus his/her attention only on those answers that have not been predicted a zero grade by the model.

>>>>

The next answer is an example of an answer that the lecturer had given zero points (i.e., the lowest possible score).

@@

Even given the limitations described above, a model does not have to be perfect in order to be of potential use. For example, if it is able to detect which answers are excellent (i.e., worth a 10), and/or which answers are plain wrong (i.e., worth a 0), it could single out those answers and leave the rest for the lecturer to grade manually. From Figures \ref{lda}, \ref{lsa} and \ref{baseline} it can be seen that it is already the case that whenever a model had assigned a zero to a student answer, the lecturer had also assigned a zero. Thus, the current models \textit{are} good enough to automatically detect which answers are worth zero points. However, it should be noted that many (although not all) of these `answers' were in fact blank answers, which of course makes their grading rather trivial.
